Codebook
========
Codebook was generated on `r as.character(Sys.time())` at the same time as the data set generation.

Description of variables
------------------------

Variable name    | Description
-----------------|------------
subject          | ID the subject who performed the activity for each window sample (1 to 30)
activity         | Name of the activity
domain       	 | Feature: time domain signal or frequency domain signal (Time or Frequency)
instrument   	 | Feature: measuring instrument used to measure (Accelerometer or Gyroscope)
acceleration 	 | Feature: signal for the acceleration (Body or Gravity)
variable     	 | Feature: variable (Mean or Std)
jerk         	 | Feature: jerk signal (Jerk or NA)
magnitude    	 | Feature: magnitude of the signals calculated using the Euclidean norm (Magnitude or NA)
axis         	 | Feature: 3-axial signals in the X, Y and Z directions (X, Y, Z, or NA)
mean        	 | Average of each variable for each activity and each subject



Additional information
----------------------

* Dataset structure

```{r}
str(tidydf)
```

* List columns in the data table

```{r}
names(tidydf)
```

* Show a few rows of the dataset

```{r}
head(tidydf)
```

* Summary of variables

```{r}
summary(tidydf)
```

